Explaining NonLinear Classification Decisions with Deep Taylor Decomposition

### 2022-06-12 Präsentation/Präsentation_23.06.2020.tex
präsi

\setbeamercolor{frametitle}{fg=black,bg=white}

\usetheme{CambridgeUS}
\usepackage{ngerman}
\renewcommand{\figurename}{Figure}
\renewcommand{\tablename}{Tabel}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

\begin{document}
\title[Deep Taylor Decomposition]{Explaining NonLinear Classification Decisions with Deep Taylor Decomposition\\
analysis}  
\author{Marcel Pommer}
\institute{LMU M\"unchen}
\date{\today}

@@

\begin{frame}
\frametitle[Explainability]{Explainability}
\begin{center}
\includegraphics[width=0.9\textwidth]{image/introduction_image}
\end{center}
\vspace{0.25cm}
Deep neural networks have great performance on a variety of problems \\
\textbf{but} how can we justify decisions made by complex deep architectures?\\
\end{frame}

@@

\subsection[interpretable classifier]{Interpretable Classifier}
\begin{frame}
\frametitle{Interpretable Classifier} 
\vspace{0.5cm}
Explanation of non-linear classification in terms of the inputs\\
$\rightarrow$ A classifier should not only provide a result but also a reasoning

@@

\subsection[General Idea]{General Idea}

\begin{frame}
\frametitle{General Idea} 
\vspace{0.35cm}
To accomplish the task of explainability we map relevance from the output to the input features

@@

\begin{center}
\begin{figure}
\includegraphics[height=4.5cm, width=11cm]{image/fig._1_example}
\caption{NN detecting 0 while distrected by 5}
\end{figure}
\end{center}

@@

\begin{frame}
\frametitle{Mathematical Framework}
\vspace{0.5cm} 
In the context of image classification we define the following mathematical framework
\begin{itemize}
\item Positive valued function $f:\mathbb{R}^d\to \mathbb{R}^+$, where the output $f(x)$ defines either the probability that the object is present or the quantity of the object in question
\item[$\rightarrow$] $f(x)>0$ expresss the presence of the object  
\item Input $x \in \mathbb{R}^d$, composable in a set of pixel values $x=\{x_p\}$
\item Relevance score $R_p(x)$ indicating the relevance of each pixel
\item[$\rightarrow$] The relevance score can be displayed in a heatmap denoted by $R(x) = \{R_P(x)\}$
\end{itemize}

\begin{figure}
\includegraphics[height=2cm, width=2cm]{image/heatmap_example}
\end{figure}

@@

@@

\begin{frame}
\frametitle{Definitions}
Further we test all algorithms for compliance with definition 1 and 2 why we introduce the definition of consistency which forth on is a measure of correctness of a technique\\
%\vspace{0.1cm}

@@

\vspace{0.5cm}
However consistency is not a measure of quality which can be seen easily on the following example which complies with definition 3
\begin{equation*}
\forall p: R_p(x) =\frac{1}{d} \dot f(x) ,
\end{equation*}
where d denotes the number of pixels
\end{frame}

@@

\begin{frame}
\frametitle{Taylor Expansion}
\vspace{0.35cm}
First order taylor expansion at root point $\tilde{x}$
\begin{flalign*}
 f(x) & =f(\tilde{x}) + \left( \frac{\partial f}{\partial x}\Big|_{x=\tilde{x}}\right)^T \cdot (x-\tilde{x}) + \epsilon\\
       & = 0 + \sum_p \underbrace{\frac{\partial f}{\partial x_p}\Big|_{x=\tilde{x}} \cdot (x_p-\tilde{x_p})}_{R_p(x)} + \epsilon  
\end{flalign*}
The challenge of finding a root point
 \begin{columns}
          \begin{column}[T]{5.5cm}
             \begin{figure}
             \includegraphics[height=2.75cm, width=6cm]{image/fig._2_example_root_point}
             \end{figure}
            \end{column} 
            \begin{column}[T]{6.2cm}
			\begin{itemize}
			\item Potentially more than one root point
			\item Remove object but deviate as few as possible
			\item[$\rightarrow$] $\min_{\xi} ||\xi-x||^2 \text{ subject to } f(\xi)=0$
			\end{itemize}
	\end{column}
\end{columns}

@@

\begin{frame}
\frametitle{Sensitivity Analysis}
Choose a root point at infinitisimally small distance from the actual point, i.e. $\xi = x- \delta \frac{\partial f}{\partial x}$\\
If we assume a locally constant function we get
\begin{flalign*}
 f(x) & =f(\xi) + \left( \frac{\partial f}{\partial x}\Big|_{x=\xi}\right)^T \cdot (x- (x- \delta \frac{\partial f}{\partial x})) + 0\\
       & = f(\xi) + \delta \left( \frac{\partial f}{\partial x}\right)^T  \frac{\partial f}{\partial x} + 0\\
       & = f(\xi) + \sum_p \underbrace{ \delta \left( \frac{\partial f}{\partial x}\right)^2}_{R_p} + 0
\end{flalign*}

\begin{itemize}
\item The heatmap is positive but not conservative
\item Measure local effect
\end{itemize}

@@

\begin{frame}
\frametitle{Deep Taylor Decomposition}
\vspace{0.25cm}
\begin{figure}
\includegraphics[height=2.75cm, width=11cm]{image/deep_taylor_decomposition_example}
 \end{figure}
We view each layer as a seperate function and write the Taylor decomposition of $\sum_j R_j \text{ at } \{x_i\}$ as
\begin{align*}
    \sum_j R_j &= \left( \frac{\partial (\sum_j R_j)}{\partial \{x_i\}}\Big|_{\{\tilde{x_i}\}}\right)^T \cdot (\{x_i\}-\{\tilde{x}\}) + \epsilon\\
    &= \sum_i \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}\}} \cdot (x_i-\tilde{x_i}) + \epsilon
\end{align*}

@@

\begin{itemize}
\item  If each local Taylor decomposition is \textit{conservative} then the chain of equalitis is also \textit{conservative} (Layer-wise relevance conservation)
\item[$\rightarrow$] $R_f = ...= \sum_i R_i = ... = \sum_p R_p$
\item  If each local Taylor decomposition is \textit{positive} then the chain of equalitis is also \textit{positive} 
\item[$\rightarrow$] $R_f,...,\{R_i\},...,\{R_P\} \geq 0$
\item If each local Taylor decomposition is \textit{consistent} then the chain of equalitis is also \textit{consistent} 
\end{itemize}

@@

\begin{frame}
\frametitle{Setting}
\vspace{0.2cm}
Consider a simple detection-pooling one layer neural network with
 \begin{columns}
          \begin{column}[T]{5.5cm}
		\begin{align*}
		x_j &= \max(0, \sum_i x_iw_{ij} + b_j)\\
		x_k &= \sum_j x_j, \ b_j \leq 0, \forall j
		\end{align*}
            \end{column} 
            \begin{column}[T]{6.5cm}
			\begin{figure}
				\includegraphics[height=2.5cm, width=6cm]{image/one_layer_nn}
			\end{figure}
	\end{column}
\end{columns} 
\begin{enumerate}
\item $R_k = x_k$ and thus $R_k = \sum_j x_j$
\item  Chose a root point and redistribute $R_k$ on neurons $x_j$\\
$\rightarrow$ $R_j = \frac{\partial R_k}{\partial x_j}\Big|_{\{\tilde{x}_j\}} \cdot (x_j - \tilde{x}_j) $, with $\{x_j\}=0$
\item Since $\frac{\partial R}{\partial x_j}=1$ we obtain $R_j = x_j$
\item Apply Taylor decomposition another time and get\\
 $R_i = \sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)})$
\end{enumerate}

@@

\begin{frame}
\frametitle{Derivation of Propagation Rules}
Given $R_j = \max(0, \sum_i x_iw_{ij} + b_j)$ and $b_j <0$ and a search direction $\{v_i\}^{(j)}$ in the input space such that
\vspace{-0.35cm}
\begin{equation}
\{\tilde{x}\}^{(j)} = \{x_i\} + t \{v_i \} ^{(j)} \Leftrightarrow t = \frac{\tilde{x_i}^{(j)} - x_i}{v_i^{(j)}}
\label{equ:search_direction}
\end{equation}
\vspace{-0.35cm}

If the data point itself is not a root point, i.e. $\sum_i x_i w_{ij} + b_j>0$ the nearest root along $\{v_i\}^{(j)}$ is given by the intersection of equation \eqref{equ:search_direction} and $\sum_i\tilde{ x_i}^{(j)} w_{ij} + b_j=0$ which can be resolved to 
\vspace{-0.25cm}
\begin{align*}
0 &= \sum_i\{x_i\}w_{ij} + b_j + \sum_i v_i^{(j)} t \\
x_i - \tilde{x_i}^{(j)} & = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
\end{align*}

@@

\begin{frame}
\frametitle{Derivation of Propagation Rules}
\vspace{0.4cm}
Starting from the Taylor expansion we can plug in 
\begin{align*}
x_i - \tilde{x_i}^{(j)} = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
\end{align*}
\vspace{-0.2cm}
To get
\vspace{-0.2cm}
\begin{align*}
R_i & = \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i^{(j)}} \dot (x_i - \tilde{x}_i^{(j)})= \sum_j w_{ij}\frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}\\
&= \sum_j w_{ij}\frac{v_i^{(j)} w_{ij}}{\sum_i v_i^{(j)} w_{ij}} R_j \numberthis \label{equ:relevance_model}
\end{align*}

The relevance propagation rule can now easily be calculated by defining
\begin{enumerate}
	\item Define a segment with search directio $\{v_i\}^{(j)}$
	\item The line lies inside the input domain and contains a root point
	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}
\end{frame}

@@

\begin{frame}
\frametitle{$w^2$-rule $\mathcal{X}=\mathbb{R}^d$}
Choose root point which is nearest in euclidean sense\\
\begin{enumerate}
	\item Search direction $\{v_i\}^{(j)} = w_{ij}$
	\item No domain restriction
	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}

\begin{block}{$w^2$-rule}
\begin{equation*}
R_i =\sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)}) =  \sum_j\frac{w_{ij}^2}{\sum_i w_{ij}^2} R_j
\end{equation*}
\end{block}

@@

\begin{frame}
\frametitle{$w^2$-rule $\mathcal{X}=\mathbb{R}^d$}
\vspace{0.3cm}
\begin{block}{Proposition 1}
For all function $g \in G$, the deep Taylor decomposition with the $w^2$-rule is consistent.
\end{block}
\textbf{Proof}\\
\begin{enumerate}
\item \textit{Conservative}
\begin{align*}
\sum_i R_i &= \sum_i\Big(\sum_j \frac{w_{ij}^2}{\sum_iw_{ij}^2}R_j\Big)\\
   		&= \sum_j \frac{\sum_i w_{ij}^2}{\sum_iw_{ij}^2}R_j = \sum_j R_j = \sum_j x_j = f(x)
\end{align*}
\item \textit{Positive}
\begin{align*}
R_i = \sum_j \frac{w_{ij}^2}{\sum_i w_{ij}^2}R_j = \sum_j \underbrace{w_{ij}^2}_{>0}  \underbrace{\frac{1}{\sum_i w_{ij}^2}}_{>0}  \underbrace{R_j}_{\geq 0} \geq 0
\end{align*}
\end{enumerate}

@@

\begin{frame}
\frametitle{$z^+$-rule $\mathcal{X}=\mathbb{R}^d_+$}
\vspace{-0.4cm}
\begin{block}{Proposition 2}
For all function $g \in G$ and data points $\{x_i\} \in \mathbb{R}_+^d$, the deep Taylor decomposition with the $z^+$-rule is consistent.
\end{block}
\vspace{0.5cm}
\textbf{Proof}\\
If $\sum_i x_i w_{ij}^+ >0$ the same proof as for the $w^2$-rule applies, if $\sum_i x_i w_{ij}^+ =0$ follows that $\forall i: x_i w_{ij} \leq0$ and

@@

\begin{frame}
\frametitle{$z^b$-rule $\mathcal{X}=\mathcal{B}$}
\vspace{0.4cm}
Often we have a bounded input space $\mathcal{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\} $ and a segment $(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\},\{x_i\})\subset \mathcal{B}$\\
\begin{enumerate}
	\item Search direction $\{v_i\}^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}$
	\item If $\{x_i\} \in \mathcal{B}$ so is the whole domain, further for $w_{ij}^-=\min(0,w_{ij})$ and $w_{ij}^+=\max(0,w_{ij})$
	\vspace{-0.25cm}
	\begin{align*}
		R_j(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\}) &= \max(0, \sum_i l_i 1_{w_{ij}>0} w_{ij} + h_i 1_{w_{ij}<0} w_{ij} + b_j)\\
		&=\max(0, \sum_i l_i w_{ij}^+ + h_i w_{ij}^- + b_j)= 0
	\end{align*}
	\vspace{-0.25cm}
	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}
\vspace{-0.25cm}

\begin{block}{$z^b$-rule}
\begin{equation*}
R_i =  \sum_j \frac{x_i w_{ij} - l_i w_{ij}^+ - h_i w_{ij}^-}{\sum_{i'} x_{i'} w_{i'j}  - l_i w_{i'j}^+ - h_i w_{i'j}^-} R_j
\end{equation*}
\end{block}

@@

\section[ausschlie{\ss}lich Allgemeinwohl]{Die Implementierung des PT ist unm\"oglich, wenn alle Agenten ausschlie{\ss}lich am Allgemeinwohl interessiert sind}

\section[alternatives privates Motiv]{Diskussion: Ein Vorschlag zur Umformulierung des privaten Motivs}

\subsection{Ein alternatives privates Motiv}
\begin{frame}\frametitle{Ein alternatives privates Motiv}
\vspace{-1.2cm}
\textbf{Das alternative private Motiv:} Jeder Agent ist neben dem Allgemeinwohl daran interessiert, dass sich seine Empfehlung ex post als richtig erweist.
\vspace{0.4cm}
\begin{block}{Behauptung}
Der in Kapitel drei definierte Mechanismus implementiert das PT f\"ur jedes Profil von Pr\"aferenzen, das strikt wachsend im PT und dem oben definierten privaten Motiv ist.
\end{block}

@@

\begin{frame}\frametitle{Beweis}
\vspace{0.4cm}
Der Beweis erfolgt weitestgehend analog zum Beweis von Proposition 2. Im Folgenden die Unterschiede:
\begin{itemize}
\item Es gilt $\pi_1 \geq V(1)$, aber $\pi_{2,1}<1$. Trotzdem steht das private Motiv von Agent 1 dem \"offentlichen nicht entgegen.
\item [$\rightarrow$] Agent 1 maximiert $\pi_{2,1}<1$, indem er $\pi_1$ maximiert, damit w\"ahlt er $S$ so informativ wie m\"oglich.
\item Analog zum Beweis von Proposition 2 folgt damit $S_{NT}=\varnothing$.
\item Mit Hilfslemma 1 folgt ebenfalls, dass $S_c=\varnothing$, da ein Agent durch einen Wechsel von der Strategie ``c'', zur Strategie ``T'', $\pi_{2,i}$ von $\frac{1}{2}$ auf $p$ erh\"oht.
\item Da alle Agenten $i\notin S$ ausschlie{\ss}lich daran interessiert sind, dass sich ihre Empfehlung ex post als richtig erweist, spielen sie ``T''.
\item [$\rightarrow$] Damit folgt, dass Agent 1 $S=N\setminus \{1\}$ w\"ahlt und alle Agenten in $S$ spielen ``T''. Agent 1 folgt der Mehrheit und im Fall eines Unentschieden folgt er seinem eigenen Signal.
\end{itemize}
\end{frame}

\section{Literatur}
\begin{frame}
\frametitle{Literatur}
\footnotesize{
\begin{thebibliography}{99}
\bibitem[wik]{p1} [GR98] Jacob Glazer and Ariel Rubinstein. Motives and implementation: On the design of mechanism to elicit opinions. Journal of economic Theory, 79(2):157-173, 1998.
\end{thebibliography}
}
\end{frame}

>>>>

\setbeamercolor{frametitle}{fg=black,bg=white}
\setbeamertemplate{caption}[numbered]
\usetheme{CambridgeUS}
\usepackage{ngerman}
\renewcommand{\figurename}{Figure}
\renewcommand{\tablename}{Tabel}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\newcommand\norm[1]{\left\lVert#1\right\rVert}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[backend=biber]{biblatex}
\bibliography{literature_seminar.bib}

% Removes icon in bibliography
\setbeamertemplate{bibliography item}{}

\begin{document}
\title[Deep Taylor Decomposition]{Explaining NonLinear Classification Decisions with Deep Taylor Decomposition}  
\author{Marcel Pommer}
\institute{LMU M\"unchen}
\date{\today}

@@

\begin{frame}
\frametitle[Explainability]{Explainability}
\vspace{0.25cm}
\begin{figure}
\includegraphics[width=0.9\textwidth]{image/introduction_image}
\end{figure}
\vspace{0.25cm}
Deep neural networks performe great on a variety of problems \nocite{*}\\
\textbf{but} how can we justify decisions made by complex deep architectures?\cite{Montavon.2017b}\\
\end{frame}

@@

\begin{frame}
\frametitle{Interpretable Classifier} 
\vspace{0.5cm}
Explanation of non-linear classification in terms of the inputs\\
$\rightarrow$ A classifier should not only provide a result but also a reasoning

@@

\begin{frame}
\frametitle{General Idea} 
\vspace{0.5cm}
To accomplish the task of explainability we map relevance from the output to the input features

@@

\begin{center}
\begin{figure}
\includegraphics[height=4.5cm, width=11cm]{image/fig._1_example}
\caption{Neural Network Detecting 0 while Distrected by 5}
\end{figure}
\end{center}

@@

\begin{frame}
\frametitle{Mathematical Framework}

In the context of image classification we define the following mathematical framework
\begin{itemize}
\item Positive valued function $f:\mathbb{R}^d\to \mathbb{R}^+$, where the output $f(x)$ defines either the probability that the object is present or the quantity of the object in question
\item[$\rightarrow$] $f(x)>0$ expresses the presence of the object

\end{itemize}

 \begin{columns}
          \begin{column}[T]{8cm}
          		\begin{itemize}
          		\item Input $x \in \mathbb{R}^d$, composable in a set of pixel values $x=\{x_p\}$
			\item Relevance score $R_p(x)$ indicating the relevance of each pixel
			\item[$\rightarrow$] The relevance score can be displayed in a heatmap denoted by $R(x) = \{R_P(x)\}$
			\end{itemize}

            \end{column} 
            \begin{column}[T]{3.5cm}
			\begin{figure}
			\includegraphics[height=2.75cm, width=2.75cm]{image/heatmap_example}
			\end{figure}
	\end{column}
\end{columns}

@@

\vspace{0.5cm}

@@

\begin{frame}
\frametitle{Definitions}
Further we test all algorithms for compliance with definition 1 and 2 hence we introduce the definition of consistency which forth on is a measure of correctness of a technique\\
\vspace{0.1cm}

@@

\vspace{0.5cm}
However consistency is not a measure of quality which can be seen easily on the following example which complies with definition 3
\begin{equation*}
\forall p: R_p(x) =\frac{1}{d} \cdot f(x) ,
\end{equation*}
where d denotes the number of pixels
\end{frame}

@@

\begin{frame}
\frametitle{Taylor Expansion}
\vspace{0.35cm}
First order taylor expansion at root point $\tilde{x}$
\begin{flalign*}
 f(x) & =f(\tilde{x}) + \left( \frac{\partial f}{\partial x}\Big|_{x=\tilde{x}}\right)^T \cdot (x-\tilde{x}) + \epsilon\\
       & = 0 + \sum_p \underbrace{\frac{\partial f}{\partial x_p}\Big|_{x=\tilde{x}} \cdot (x_p-\tilde{x_p})}_{R_p(x)} + \epsilon  
\end{flalign*}
The challenge of finding a root point
 \begin{columns}
          \begin{column}[T]{5.5cm}
             \begin{figure}
             \includegraphics[height=2.75cm, width=6cm]{image/fig._2_example_root_point}
             \end{figure}
            \end{column} 
            \begin{column}[T]{6.2cm}
			\begin{itemize}
			\item Potentially more than one root point
			\item Remove object but deviate as few as possible
			\item[$\rightarrow$] $\min_{\xi} \norm{\xi-x}^2 \text{subject to } f(\xi)=0$
			\end{itemize}
	\end{column}
\end{columns}

@@

\begin{frame}
\frametitle{Sensitivity Analysis}
\vspace{0.25cm}
Root point at infinitisimally small distance from the actual point, i.e. $\xi = x- \delta \frac{\partial f}{\partial x}$, where $\delta$ is small\\
\vspace{0.1cm}
If we assume a locally constant function we get
\begin{flalign*}
 f(x) & =f(\xi) + \left( \frac{\partial f}{\partial x}\Big|_{x=\xi}\right)^T \cdot (x- (x- \delta \frac{\partial f}{\partial x})) + 0\\
       & = f(\xi) + \delta \left( \frac{\partial f}{\partial x}\right)^T \cdot  \frac{\partial f}{\partial x} + 0\\
       & = f(\xi) + \sum_p \underbrace{ \delta \left( \frac{\partial f}{\partial x}\right)^2}_{R_p} + 0
\end{flalign*}

\begin{itemize}
\item The heatmap is positive but not conservative
\item The heatmap only measures a local effect
\end{itemize}

@@

\begin{frame}
\frametitle{Deep Taylor Decomposition}
\vspace{0.25cm}
\begin{figure}
\includegraphics[height=2.75cm, width=11cm]{image/deep_taylor_decomposition_example}
 \end{figure}
\vspace{0.25cm}
We view each layer as a seperate function and write the Taylor decomposition of $\sum_j R_j \text{ at } \{x_i\}$ as
\begin{align*}
    \sum_j R_j &= \left( \frac{\partial (\sum_j R_j)}{\partial \{x_i\}}\Big|_{\{\tilde{x_i}\}}\right)^T \cdot (\{x_i\}-\{\tilde{x}\}) + \epsilon\\
    &= \sum_i \underbrace{\sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}\}} \cdot (x_i-\tilde{x_i})}_{R_i} + \epsilon
\end{align*}
\vspace{-0.25cm}

@@

\begin{itemize}
\item  If each local Taylor decomposition is \textit{conservative} then the chain of equalities is also \textit{conservative} (layer-wise relevance conservation)
\item[$\rightarrow$] $R_f = ...= \sum_i R_i = ... = \sum_p R_p$
\item  If each local Taylor decomposition is \textit{positive} then the chain of equalities is also \textit{positive} 
\item[$\rightarrow$] $R_f,...,\{R_i\},...,\{R_P\} \geq 0$
\item If each local Taylor decomposition is \textit{consistent} then the chain of equalities is also \textit{consistent} 
\end{itemize}

@@

\begin{frame}
\frametitle{Setting}
\vspace{0.5cm}
Consider a simple detection-pooling one layer neural network with
\vspace{-0.2cm}
 \begin{columns}
          \begin{column}[T]{5.5cm}
		\begin{align*}
		x_j &= \max(0, \sum_i x_iw_{ij} + b_j)\\
		x_k &= \sum_j x_j, \ b_j \leq 0, \forall j
		\end{align*}
            \end{column} 
            \begin{column}[T]{6.5cm}
			\begin{figure}
				\includegraphics[height=2.5cm, width=6cm]{image/one_layer_nn}
			\end{figure}
	\end{column}
\end{columns} 
\vspace{0.25cm}
\begin{enumerate}
\item $R_k = x_k$ and thus $R_k = \sum_j x_j$
\item  Chose a root point and redistribute $R_k$ on neurons $x_j$\\
$\rightarrow$ $R_j = \frac{\partial R_k}{\partial x_j}\Big|_{\{\tilde{x}_j\}} \cdot (x_j - \tilde{x}_j) $, with $\{\tilde{x}_j\}=0$
\item Since $\frac{\partial R_k}{\partial x_j}=1$ we obtain $R_j = x_j$
\item Apply Taylor decomposition another time and get\\
 $R_i = \sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)})$
\end{enumerate}

@@

\begin{frame}
\frametitle{Derivation of Propagation Rules}
\vspace{0.3cm}
Given $R_j = \max(0, \sum_i x_iw_{ij} + b_j)$ and $b_j \leq 0$ and a search direction $\{v_i\}^{(j)}$ in the input space such that

\begin{equation}
\tilde{x}^{(j)} = x_i + t v_i ^{(j)} \Leftrightarrow t = \frac{\tilde{x_i}^{(j)} - x_i}{v_i^{(j)}}
\label{equ:search_direction}
\end{equation}

\vspace{0.2cm}
If the data point itself is not a root point, i.e. $\sum_i x_i w_{ij} + b_j>0$ the nearest root along $\{v_i\}^{(j)}$ is given by the intersection of equation \eqref{equ:search_direction} and $\sum_i\tilde{ x_i}^{(j)} w_{ij} + b_j=0$ which can be resolved to 
\vspace{-0.1cm}
\begin{align*}
0 &= \sum_i x_i w_{ij} + b_j + \sum_i v_i^{(j)} t \\
x_i - \tilde{x_i}^{(j)} & = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
\end{align*}

@@

\begin{frame}
\frametitle{Derivation of Propagation Rules}
\vspace{0.4cm}
Starting from the Taylor expansion we can plug in 
\begin{align*}
x_i - \tilde{x_i}^{(j)} = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
\end{align*}
\vspace{-0.2cm}
To get
\vspace{-0.2cm}
\begin{align*}
R_i & = \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)})= \sum_j w_{ij}\frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}\\
&= \sum_j\frac{v_i^{(j)} w_{ij}}{\sum_i v_i^{(j)} w_{ij}} R_j \numberthis \label{equ:relevance_model}
\end{align*}

The relevance propagation rule can be calculated with the following steps
\begin{enumerate}
	\item Define a segment with search direction $\{v_i\}^{(j)}$
	\item The line lies inside the input domain and contains a root point
	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}
\end{frame}

@@

\begin{frame}
\frametitle{$w^2$-rule $\mathcal{X}=\mathbb{R}^d$}
Choose a root point which is nearest in the euclidean sense\\

\begin{enumerate}
	\item Search direction $\{v_i\}^{(j)} = w_{ij}$ (gradient of $R_j$)
	\item No domain restriction
	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}
\vspace{0.25cm}
\begin{block}{$w^2$-rule}
\begin{equation*}
R_i =\sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)}) =  \sum_j\frac{w_{ij}^2}{\sum_{i'} w_{i'j}^2} R_j
\end{equation*}
\end{block}

@@

\begin{frame}
\frametitle{$w^2$-rule $\mathcal{X}=\mathbb{R}^d$}
\vspace{0.3cm}
\begin{block}{Proposition 1}
For all functions $g \in G$, the deep Taylor decomposition with the $w^2$-rule is consistent.
\end{block}
\textbf{Proof}\\
\begin{enumerate}
\item \textit{Conservative}
\begin{align*}
\sum_i R_i &= \sum_i\Big(\sum_j \frac{w_{ij}^2}{\sum_{i'}w_{i'j}^2}R_j\Big)\\
   		&= \sum_j \frac{\sum_i w_{ij}^2}{\sum_{i'} w_{i'j}^2}R_j = \sum_j R_j = \sum_j x_j = f(x)
\end{align*}
\item \textit{Positive}
\begin{align*}
R_i = \sum_j \frac{w_{ij}^2}{\sum_{i'} w_{i'j}^2}R_j = \sum_j \underbrace{w_{ij}^2}_{\geq 0}  \underbrace{\frac{1}{\sum_{i'} w_{i'j}^2}}_{>0}  \underbrace{R_j}_{\geq 0} \geq 0
\end{align*}
\end{enumerate}

@@

\begin{frame}
\frametitle{$z^+$-rule $\mathcal{X}=\mathbb{R}^d_+$}
\vspace{-0.4cm}
\begin{block}{Proposition 2}
For all functions $g \in G$ and data points $\{x_i\} \in \mathbb{R}_+^d$, the deep Taylor decomposition with the $z^+$-rule is consistent.
\end{block}
\vspace{0.5cm}
\textbf{Proof}\\
If $\sum_i x_i w_{ij}^+ >0$ the same proof as for the $w^2$-rule applies, if $\sum_i x_i w_{ij}^+ =0$ it follows that $\forall i: x_i w_{ij} \leq0$ and

@@

\begin{frame}
\frametitle{$z^b$-rule $\mathcal{X}=\mathcal{B}$}
\vspace{0.4cm}
Often we have a bounded input space $\mathcal{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\} $ and a segment $(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\},\{x_i\})\subset \mathcal{B}$\\
\begin{enumerate}
	\item Search direction $\{v_i\}^{(j)} = x_i - l_i 1_{w_{ij}>0} - h_i 1_{w_{ij}<0}$
	\item If $\{x_i\} \in \mathcal{B}$ so is the whole domain, further for $w_{ij}^-=\min(0,w_{ij})$ and $w_{ij}^+=\max(0,w_{ij})$
	\vspace{-0.25cm}
	\begin{align*}
		R_j(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\}) &= \max(0, \sum_i l_i 1_{w_{ij}>0} w_{ij} + h_i 1_{w_{ij}<0} w_{ij} + b_j)\\
		&=\max(0, \sum_i l_i w_{ij}^+ + h_i w_{ij}^- + b_j)= 0
	\end{align*}
	\vspace{-0.25cm}
	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}
\vspace{-0.25cm}

\begin{block}{$z^b$-rule}
\begin{equation*}
R_i =  \sum_j \frac{x_i w_{ij} - l_i w_{ij}^+ - h_i w_{ij}^-}{\sum_{i'} x_{i'} w_{i'j}  - l_i w_{i'j}^+ - h_i w_{i'j}^-} R_j
\end{equation*}
\end{block}
\end{frame}

@@

\subsection[Example MINST]{Example MNIST}

\begin{frame}
\frametitle{Example MNIST: Setting}
\vspace{0.5cm}
Training of a neural network to detect a handwritten digit between 0-3 next to a distractor digit from 4-9 given the following setting:
\begin{itemize}
\item images of size 28 x 56 pixels
\item 28 x 56 = 1568 input neurons $\{x_i\}$, one hidden layer with 400 neurons $\{x_j\}$ and one output $x_k$
\item weights are random initialized $\{w_{ij}\}$ and bias $\{b_j\}$ is initialized to zero and non negative during training
\item Training with 300000 iterations of stochastic gradient descent with a batch size of 20 
\end{itemize}
\begin{figure}
\includegraphics[height=2.5cm, width=8cm]{image/fig._1_example}

\end{figure}
\end{frame}

\begin{frame}
\frametitle{Example MNIST: Heatmaps}
\vspace{0.5cm}
\begin{figure}
\includegraphics[height=2.5cm, width=12cm]{image/example_mnist_heatmap}
\end{figure}

\begin{figure}
\includegraphics[height=3.25cm, width=12cm]{image/example_mnist_consistent}
\vspace{-0.75cm}
\caption{Heatmap and Empirical Results of Consistency}
\end{figure}

@@

\section[Application to Deep Networks]{Application to Deep Networks}

\begin{frame}
\frametitle{Deep Networks}
Many problems require very complex deep architectures

\begin{figure}
\label{fig1}
\includegraphics[height=6cm, width=11cm]{image/example_deep_network_one}
\vspace{-0.25cm}
\caption{Example Deep Network}

\end{figure}

\vspace{-1cm}
\end{frame}

\begin{frame}
\frametitle{Relevance Model}
\vspace{0.25cm}
In deep architectures as in figure 3 a mapping between two layers may be unknown, even if it exists
\begin{block}{Definition 1}
A relevance model is a function that maps a set of neuron activations at a given layer to the relevance of a neuron in a higher layer, and whose output can be redistributed onto its input variables.
\end{block}

\begin{figure}
\label{fig1}
\includegraphics[height=4cm, width=7.75cm]{image/example_deep_network_one}
\end{figure}
\vspace{-0.5cm}
\end{frame}

\begin{frame}
\frametitle{Min-Max Relevance Model}
\vspace{0.4cm}
Trainable relevance model designed to incorporate bottom-up and top-down information
\begin{align*}
y_i &= \max(0,\sum_ix_iv_{ij} + a_j)\\
\hat{R}_k &= \sum_j y_j,
\end{align*}
where $a_j = \min(0,\sum_l R_l v_{lj} + d_j)$ is a negative bias
\vspace{-0.25cm}

 \begin{columns}
          \begin{column}{5cm}
          		$\rightarrow$ Compute $\{v_{ij}, v_{lj},d_j\}$ by minimizing 
			\begin{equation*}
			\min\langle (\hat{R}_k-R_k)^2) \rangle
			\end{equation*}
            \end{column} 
            \begin{column}{6cm}
			\begin{figure}
			\label{fig1}
			\includegraphics[height=3cm, width=6.5cm]{image/min_max_relevance_model}
			\end{figure}
	\end{column}
\end{columns}

\begin{frame}
\frametitle{Min-Max Relevance Model}
Due to the similar structure we can apply the propagation rules for the one-layer neural network
\begin{itemize}
\item Pooling layer
\begin{equation*}
R_j = y_j
\end{equation*}
